My title

### 2024-03-19 paper/paper.qmd
Trying to render the tables
```{r}
chooseCRANmirror(graphics = FALSE)  # Select a CRAN mirror
install.packages("devtools")        # Install the devtools package
```

```{r}
install.packages("devtools")
install.packages("kableExtra")
devtools::install_github("haozhu233/kableExtra")
```

>>>>

```{r}
chooseCRANmirror(graphics = FALSE)  # Select a CRAN mirror
install.packages("devtools")        # Install the devtools package
```

```{r}
install.packages("devtools")
install.packages("kableExtra")
devtools::install_github("haozhu233/kableExtra")
```

```{r}
library(knitr)
library(kableExtra)

library(knitr)
library(kableExtra)

# Define the list
dflist <- list(variables = c("All Americans","Race", "Gender", "Political Affiliation", "Level of Education"),
               observations = c("All the following groups", "Self identified race of participants","Male/Female","Democrat/Republican/Other", "College Degree or Higher/Highschool Diploma/ No Highschool Diploma")
              )

# Convert the list to a data frame
df <- as.data.frame(dflist)

# Transpose the data frame
df <- t(df)

# Display the transposed data frame as a table with kableExtra
kbl(df) %>%
  kable_classic(full_width = FALSE, html_font = "Cambria")

##///////////////////////////////////////////////////////////////////////////////////////////////////////////////////////

# Define the additional rows
additional_rows <- data.frame(variables = c("Banchod"),
                              observations = c("Banchod")
                             )

# Combine the original data frame with the additional rows

# Transpose the data frame
df <- t(df)

# Display the updated data frame as a table with kableExtra
kbl(df) %>%
  kable_classic(full_width = FALSE, html_font = "Cambria")
